---
title: ""
---

<BR>

# VWPre 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE)
library(VWPre)
z <- packageVersion("VWPre")
x <- browseVignettes("VWPre")
tmp <- as.data.frame(x$VWPre)
tmp <- tmp[order(tmp$Topic),]
```

```{r, eval = TRUE, echo=FALSE, results='hide', message=FALSE, cache=T}
data(VWdat)
dat <- fasttrack(data = VWdat, Subject = "RECORDING_SESSION_LABEL", Item = "itemid", 
	EventColumns = c("Subject", "TRIAL_INDEX"), NoIA = 4, Adjust = 100, Recording = "LandR", 
  WhenLandR = "Right", BinSize = 20, SamplingRate = 1000,
  ObsPerBin = 20, Constant = 0.5, Output = "ELogit")
```

<BR>
<BR>

I develop and maintain *VWPre*, an R package for preprocessing and plotting Visual World Paradigm eye-tracking data. The current version of the package (`r z`) can be found on CRAN: 
<a href="https://cran.r-project.org/web/packages/VWPre/index.html" target="_blank">VWPre R package on CRAN</a> 

```{r, eval= TRUE, fig.show='hold', fig.width = 6, fig.height=3, out.width='300px', out.height='150px', fig.align='center', results='asis', message=FALSE, warning=FALSE}
plot_avg(data = dat, type = "proportion", xlim = c(0, 1000), 
    IAColumns = c(IA_1_P = "Target", IA_2_P = "Rhyme", IA_3_P = "OnsetComp", 
                  IA_4_P = "Distractor"),
    Condition1 = NULL, Condition2 = NULL, Cond1Labels = NA, Cond2Labels = NA,
    ErrorBar = TRUE, VWPreTheme = TRUE)
```

There are several elaborated vignettes designed to help the user become comfortable with the functionality of the package. Currently there are `r nrow(tmp)` vignettes available:

```{r, echo=FALSE, results="asis",comment=FALSE}

for(i in 1:nrow(tmp)) {
  cat(paste0('<a href="https://cran.r-project.org/web/packages/VWPre/vignettes/', tmp[i,3], '.html" target="_blank">', tmp[i,5], '</a>'), "\n \n")
}
# <a href="https://cran.r-project.org/web/packages/VWPre/vignettes/SR_Basic_Preprocessing.html" target="_blank">Basic VWP Preprocessing for SR Eyelink Data</a>
# 
# <a href="https://cran.r-project.org/web/packages/VWPre/vignettes/SR_Interest_Areas.html" target="_blank">Relabeling Interest Areas or Defining New Post-hoc Interest Areas for SR Eyelink Data</a>
# 
# <a href="https://cran.r-project.org/web/packages/VWPre/vignettes/SR_Message_Alignment.html" target="_blank">Aligning Sample Data to a Specific Sample Message in SR Eyelink Data</a>
# 
# <a href="https://cran.r-project.org/web/packages/VWPre/vignettes/SR_Plotting.html" target="_blank">Plotting SR Eyelink Data Processed with VWPre</a>

```

<BR>

<img src="http://cranlogs.r-pkg.org/badges/VWPre" align="bottom" height="25" width="150"> 
<BR>
<BR>

The package can be cited as below:
```{r, echo=FALSE, results="asis", comment=FALSE}
citation(package = "VWPre")
```

<BR>
<BR>